Railway: Adaptive Disk Storage for Interaction Graphs

### 2014-09-11 docs/edbt2015/text/paper.tex
started intro, 'outlined' remaining parts
paper skeleton

\section{Introduction}

\section{System Overview}

\begin{alltt}\scriptsize
- Intro
    - What is an interaction graphs
    - Relationship graphs vs interaction graphs 
        - interactions get big
- System overview
    - How interaction graph are currently stored
    - Introduce the rail layout
- Layout or partitioning problem 
    - Cost model
- Optimal Solutions
- Heuristic solutions
- Evaluation
\end{alltt}

\section{Related Work}

\begin{alltt}\scriptsize
Gedik et al.~\cite{gedik14}
H2O \cite{alagiannis14}
HYRISE~\cite{grund10}
Bornea et al.~\cite{bornea13}
\end{alltt}

\section{Conclusion}

>>>>

\input{introduction}

\begin{alltt}\scriptsize
- Intro
    - What is an interaction graphs
    - Relationship graphs vs interaction graphs 
        - interactions get big
\end{alltt}

\input{system.tex}
\input{problem.tex}
\input{optimal.tex}
\input{heuristic.tex}
\input{evaluation.tex}
\input{related.tex}
\input{conclusion.tex}
